### 2018-03-15 paper/4-build.tex
Add 3x3 table

>>>>

\subsection{Summary}

\todo{AM/NM/SLPJ}{Add a decription for the table.}

\begin{table}[h]
\smaller
\centering
\begin{tabular}{l||c|c|c}
\hline
Property           & Topological & Reordering & Recursive    \\\hline
\hline
Dirty bit          & \Make                   & \Excel                   & \Shake without early cutoff \\\hline
Verifying trace    & \Make with early cutoff & \Excel with early cutoff & \Shake                      \\\hline
Constructive trace & \Bazel                  & Cloud \Excel             & Cloud \Shake                \\\hline
\end{tabular}
\vspace{0.5mm}
\caption{Build systems \`a la carte.\label{tab-build-systems}}
\end{table}
